Labeled object representation and manipulation with ITK

### 2007-08-16 article/Article.tex
minor corrections
darcs-hash:20070816123635-2fc9d-3e4c7401a9abb4ac53181fad56e61bc0c99bf75e.gz

Richard Beare has recently introduced a new filter to efficiently labelize the
connected component with ITK, and has also proposed to use the run-length
encoding used in that filter to implement some of the most useful binary
mathematical morphology operators: the opening by attribute.
Following that idea, and after have searched a way to use the ITK's spatial
objects for this task, a new set of classes have been developed to represent and
manipulate the labeled images and the objects within them in ITK.
Those new classes have been used to implement several labeled images
manipulation based on object attributes, as well as the binary specialization of
some mathematical morphology filter already include in ITK, and not related to
the attribute of the objects. With those last filters, this contribution comes
with 49 new classes, and should greatly enhance the binary mathematical
morphology in ITK.

All the source codes are provided, as well as a full set of test and several
usage examples of the new classes.

>>>>

Richard Beare has recently introduced a new filter to efficiently labelize the
connected component with ITK, and has also proposed to use the run-length
encoding used in that filter to implement some of the most useful binary
mathematical morphology operators: the opening by attribute.
Following that idea, and after have searched a way to use the ITK's spatial
objects for this task, a new set of classes have been developed to represent and
manipulate the labeled images and the objects within them in ITK.
Those new classes have been used to implement several labeled images
manipulation based on object attributes, as well as the binary specialization of
some mathematical morphology filter already included in ITK, and not related to
the attribute of the objects. With those last filters, this contribution comes
with 49 new classes, and should greatly enhance the binary mathematical
morphology in ITK.

All the source codes are provided, as well as a full set of tests and several
usage examples of the new classes.
